\documentclass{resume}

\makeatletter
\let\@addressfour\relax

\renewcommand{\address}[1]{%
  \@ifundefined{@addresstwo}{\def\@addresstwo{#1}}{%
  \@ifundefined{@addressthree}{\def\@addressthree{#1}}{%
  \@ifundefined{@addressfour}{\def\@addressfour{#1}}{%
     \def\@addressone{#1}}}}%
}

% Re-patch \document so it also prints the 4th address
\renewcommand{\document}{%
  \ori@document
  \printname
  \@ifundefined{@addressone}{}{\printaddress{\@addressone}}%
  \@ifundefined{@addresstwo}{}{\printaddress{\@addresstwo}}%
  \@ifundefined{@addressthree}{}{\printaddress{\@addressthree}}%
  \@ifundefined{@addressfour}{}{\printaddress{\@addressfour}}%
}
\makeatother

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{romannum}

\usepackage[
    backend=biber,
    style=ieee,
    sorting=ydnt,
    maxbibnames=99,
    doi=true,
    url=true,
    isbn=false,
    defernumbers=true
]{biblatex}

\AtEveryBibitem{\clearfield{labelnumber}\clearfield{prefixnumber}}

\addbibresource{publications.bib}

% Plain section for publications, because normal rSection is already a list
\newenvironment{rSectionPlain}[1]{
  \sectionskip
  \MakeUppercase{\bf #1}
  \sectionlineskip
  \hrule
  \vspace{0.3em}
}{
  \par
}

\defbibenvironment{bibliography}
  {\list
     {\textbullet}
     {\setlength{\labelwidth}{0.5em}%
      \setlength{\labelsep}{0.5em}%
      \setlength{\leftmargin}{1.5em}%
      \setlength{\itemsep}{0.6\baselineskip}%
      \setlength{\parsep}{0pt}%
      \renewcommand*{\makelabel}[1]{##1\hss}}}
  {\endlist}
  {\item}

  

\usepackage{xstring}

\renewcommand*{\mkbibnamefamily}[1]{%
  \IfSubStr{\namepartfamily}{Ghaffari}{\mkbibbold{#1}}{#1}%
}
\renewcommand*{\mkbibnamegiven}[1]{%
  \IfSubStr{\namepartfamily}{Ghaffari}{\mkbibbold{#1}}{#1}%
}

\name{Amirhossein Ghaffari}

\address{Email: \href{mailto:amirhossein.ghaffari@oulu.fi}{amirhossein.ghaffari@oulu.fi}}
\address{LinkedIn: \href{https://www.linkedin.com/in/amirhosseinghaffari/}{linkedin.com/in/amirhosseinghaffari}}
\address{Webpage: \href{https://ahghaffari.github.io/amirhosseinghaffari/}{ahghaffari.github.io/amirhosseinghaffari}}
\address{Phone: [+358] 41 5823802}

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\vspace{+.1cm}

{\bf Doctoral Degree in Computer Science and Engineering} \hfill {\em 2023--Present} \\
\href{https://www.oulu.fi/}{University of Oulu}, Oulu, Finland \\
GPA: 4.4/5

{\bf M.Sc. in Electrical Engineering -- Digital Electronic Systems} \hfill {\em 2017--2019} \\
\href{http://www.en.sharif.edu/}{Sharif University of Technology}, Tehran, Iran \\
GPA: 18.20/20

{\bf B.Sc. in Electrical Engineering} \hfill {\em 2012--2017} \\
\href{https://www.aut.ac.ir/en}{Amirkabir University of Technology (Tehran Polytechnic)}, Tehran, Iran \\
GPA: 16.24/20

{\bf High School Diploma in Mathematics and Physics} \hfill {\em 2008--2012} \\
Roshd1 Educational Complex, Tehran, Iran \\
GPA: 19.87/20

\end{rSection}

%----------------------------------------------------------------------------------------
%   RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}
\vspace{+.1cm}

Urban Well-being \\
Machine Learning \\
Graph Neural Networks

\end{rSection}

%----------------------------------------------------------------------------------------
%   RESEARCH AND PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Research and Professional Experience}
\vspace{+.1cm}

\begin{rSubsection}{Doctoral Researcher}{\em Spring 2023--Present}
{\href{https://www.oulu.fi/}{University of Oulu}}{Oulu, Finland}
    \item Conducting doctoral research in urban well-being, machine learning, graph neural networks, multi-source urban data, and data-driven analysis of smart city systems.
\end{rSubsection}

\begin{rSubsection}{Computer Vision and Deep Learning Researcher}{\em Winter 2019--Spring 2023}
{\href{https://en.towzin.com/}{Fard Iran Co.}}{Tehran, Iran}
    \item Designed and implemented an algorithm for an Automatic Number Plate Recognition system.
    \item Designed and implemented motion detection and human detection applications for surveillance systems.
    \item Designed and implemented an algorithm to automatically optimize camera parameters, including gain and shutter speed, ensuring the capture of high-quality car license plate images throughout the day and night.
    \item Designed and implemented a signal processing tool using neural networks to measure vehicle weights in a Weigh In Motion (WIM) system.
    \item Designed and implemented a driver assistance tool to detect abnormal driving using deep learning, GPS sensor data, and ECU information for comprehensive driving analysis.
    \item Contributed to the large-scale successful deployment of 70+ Weigh In Motion (WIM) sites across Iran; participated in on-site installation, system debugging, performance optimization, and technical support to ensure operational reliability.
\end{rSubsection}

\begin{rSubsection}{Deep Learning Researcher}{\em Spring 2020--Winter 2022}
{\href{http://iwe.sharif.edu/}{Institute of Water and Energy}, Sharif University of Technology}{Tehran, Iran}
    \item Designed and implemented algorithms using deep learning and machine learning methods for an air pollution prediction system.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   THESIS PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Thesis Projects}
\vspace{+.1cm}

\begin{rSubsection}{M.Sc. Thesis}{\em 2017--2019}
{360-degree Video Transmission over Network using Coded Caching}  

    \item Supervisor: Dr. Mohammad Sharifkhani.
\end{rSubsection}

\pagebreak

\begin{rSubsection}{B.Sc. Thesis}{\em 2016--2017}
{Design and Fabrication of an Active Noise Cancellation System for Environmental Disturbing Sounds}

    \item Supervisor: Prof. Hassan Kaatuzian.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}
\vspace{+.1cm}

\begin{rSubsection}{Teaching Assistant}{\em Spring 2026, 2025, 2024}
{Big Data Processing and Applications, M.Sc. Course}{University of Oulu}
    \item Faculty of Information Technology and Electrical Engineering (ITEE).
    \item Instructor: Dr. Ekaterina Gilman.
\end{rSubsection}

\begin{rSubsection}{Teaching Assistant}{\em Spring 2025}
{Network Analysis and Graph Machine Learning, M.Sc. Course}{University of Oulu}
    \item Faculty of Information Technology and Electrical Engineering (ITEE).
    \item Instructor: Prof. Joydeep Chandra.
\end{rSubsection}

\begin{rSubsection}{Teaching Assistant}{\em Spring 2019}
{Computer Vision, M.Sc. Course}{Sharif University of Technology}
    \item Electrical Engineering Department.
    \item Instructor: Dr. Hoda Mohammadzadeh.
\end{rSubsection}

\begin{rSubsection}{Teaching Assistant}{\em Fall 2018}
{Computer Architecture, B.Sc. Course}{Sharif University of Technology}
    \item International Campus.
    \item Instructor: Dr. Hamed Farbeh.
\end{rSubsection}

\begin{rSubsection}{Teaching Assistant}{\em Fall 2018}
{Advanced Computer Architecture, M.Sc. Course}{Sharif University of Technology}
    \item Electrical Engineering Department.
    \item Instructor: Dr. Mohammadreza Movaheddin.
\end{rSubsection}

\begin{rSubsection}{Mathematics and Physics Teacher}{\em 2012--2015}
{Roshd1 Educational Complex}{Tehran, Iran}
    \item Taught mathematics and physics.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSectionPlain}{Publications}

\nocite{*}
\printbibliography[heading=none]

\end{rSectionPlain}
%----------------------------------------------------------------------------------------
%   CONFERENCES, WORKSHOPS, AND SUMMER SCHOOLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Conferences, Workshops, and Summer Schools}
\vspace{+.1cm}

\begin{itemize}

    \item {\bf ACM CIKM 2025}, Seoul, South Korea. Participated as a student volunteer and first-author presenter of a paper. {\em Fall 2025}

    \item {\bf IEEE ICNSC 2025}, Oulu, Finland. Participated as an author of a paper. {\em Fall 2025}

    \item {\bf NVIDIA Workshop}, University of Oulu, Finland. Participated in the NVIDIA workshop on Fundamentals of Accelerated Computing with CUDA Python. {\em Fall 2024}

    \item {\bf ACM IoT 2024}, Oulu, Finland. Participated as a student volunteer helping the organizing committee. {\em Fall 2024}

    \item {\bf ACM KDD 2024}, Barcelona, Spain. Full participation with a poster presentation. {\em Fall 2024}

    \item {\bf 12\textsuperscript{th} UBISS Summer School }, University of Oulu, Finland. Full participation and worked as a liaison student helping organizers in the ``Care-full! More-than-human Urban Futures'' workshop. {\em Summer 2024}

    \item {\bf 6G Symposium}, Levi, Finland. Full participation. {\em Spring 2024}

    \item {\bf IEEE PerCom 2024}, Biarritz, France. Full participation with a poster presentation. {\em Spring 2024}

    \item {\bf 11\textsuperscript{th} UBISS Summer School}, University of Oulu, Finland. Full participation in the ``Smart Internet of Things (IoT) Wireless Connectivity in 5G and Beyond'' workshop. {\em Summer 2023}

    \item {\bf IEC2-2019 Sharif}, Sharif University of Technology, Tehran, Iran. Attended KNIME, Tableau, and Pandas workshops. {\em Summer 2019}

    \item {\bf Deep Learning Summer School}, University of Tehran, Tehran, Iran. {\em Summer 2018}

    \item {\bf TensorFlow Workshop}, Sharif University of Technology, Tehran, Iran. {\em Summer 2018}

\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%   AWARDS AND HONORS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Honors}
\vspace{+.1cm}

\begin{itemize}

    \item Received an ACM CIKM Student Travel Grant to participate in the 34th ACM International Conference on Information and Knowledge Management (CIKM), Seoul, Republic of Korea, 2025.

    \item Received Tauno Tönning Foundation personal research grant, 2024.

    \item Received an IEEE Student Travel Grant to participate in the IEEE International Conference on Pervasive Computing and Communications (PerCom), Biarritz, France, 2024.

    \item 4-year fully funded doctoral researcher position through competitive selection at the University of Oulu.

    \item Iran's National Elites Foundation Award in 2019.

    \item Received national graduate and undergraduate full scholarships.

    \item Ranked within the top 0.5\% among more than 31,000 participants in the Iranian Electrical Engineering Graduate University entrance exam.

    \item Ranked within the top 0.5\% among more than 220,000 participants in the Iranian Mathematics and Physics University entrance exam.

\end{itemize}

\end{rSection}

\pagebreak
%----------------------------------------------------------------------------------------
%   SELECTED SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Skills}
\vspace{+.1cm}

\begin{itemize}

    \item {\bf Deep Learning \& Graph Neural Networks:} PyTorch, PyTorch Geometric, Hugging Face.

    \item {\bf Agentic AI \& Large Language Models:} LangGraph, LangChain, Google ADK, OpenAI / LLM provider APIs, RAG and GraphRAG pipelines.

    \item {\bf Big Data \& Distributed Systems:} Apache Spark, PySpark.

    \item {\bf Databases \& Knowledge Graphs:} PostgreSQL, Neo4j, Cypher, SPARQL, RDF.

    \item {\bf MLOps \& Cloud Native:} Docker, Kubernetes, Prometheus, Grafana, Weights \& Biases, Git.

    \item {\bf Programming Languages:} Python, C / C++, MATLAB.

\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%   LANGUAGES
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}
\vspace{+.1cm}

\begin{itemize}

    \item {\bf Persian:} Native

    \item {\bf English:} Full professional proficiency

    \item {\bf Finnish:} Beginner

    \item {\bf Swedish:} Beginner

\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%   REFERENCES
%----------------------------------------------------------------------------------------

\begin{rSection}{References}
\vspace{+.1cm}

\begin{itemize}

    \item {\bf Adj. Prof. Ekaterina Gilman} \\
    Adjunct Professor, Faculty of Information Technology and Electrical Engineering (ITEE), University of Oulu, Oulu, Finland \\
    Email: \href{mailto:ekaterina.gilman@oulu.fi}{ekaterina.gilman@oulu.fi} \\
    Web Page: \href{https://www.oulu.fi/en/researchers/ekaterina-gilman}{https://www.oulu.fi/en/researchers/ekaterina-gilman}

    \item {\bf Adj. Prof. Susanna Pirttikangas} \\
    Adjunct Professor, Faculty of Information Technology and Electrical Engineering (ITEE), University of Oulu, Oulu, Finland \\
    Email: \href{mailto:susanna.pirttikangas@oulu.fi}{susanna.pirttikangas@oulu.fi} \\
    Web Page: \href{https://www.oulu.fi/en/researchers/susanna-pirttikangas}{https://www.oulu.fi/en/researchers/susanna-pirttikangas}

    \item {\bf Asst. Prof. Lauri Lov\'en} \\
    Assistant Professor, Tenure Track; Head of Future Computing Group, University of Oulu, Oulu, Finland \\
    Email: \href{mailto:lauri.loven@oulu.fi}{lauri.loven@oulu.fi} \\
    Web Page: \href{https://www.oulu.fi/en/researchers/lauri-loven}{https://www.oulu.fi/en/researchers/lauri-loven}

\end{itemize}

\end{rSection}

\end{document}